### 2015-06-18 chapters/ipa_meets_unicode.tex
further testing large table
adds nasalization in diacritic ordering

Facing the problem of specifying a consistent ordering of diacritics while
developing a large database of phonological inventories from the world's
languages, \citet[540]{Moran2012} defines a set of diacritic ordering
conventions. The conventions are influenced by the linguistic literature, though
some ad-hoc decisions had to be taken.

@@

\begin{itemize}
	\item[] \textsc{Combining Diacritical Marks (above) ordering:}
	\begin{itemize}
	  \item[→] centralized <ë> \textbar{} mid-centralized <e̽>
	  \item[→] extra short <ĕ>
%	  \item[→] (tone accents, e.g. <è>)
	  \item[→] unreleased <p̚>
%	  \item[→] Spacing Modifier Letters, see above	  
 \end{itemize} \end{itemize}

@@

\begin{table}[htdp]

 \topcaption{IPA letters with Unicode encodings}
 \label{tab:ipa_letters}
 \tablehead{
   \toprule
   & Code & Unicode name & IPA name \\
  \midrule
  }
 \tabletail{\endline}

@@

\begin{xtabular}{ll>{\small}p{4cm}>{\small}l}

@@

ⱱ & \uni{2C71} & \textsc{latin small letter v with right hook} & voiced labiodental tap \\ 

@@

\end{table}

>>>>

Facing the problem of specifying a consistent ordering of diacritics while
developing a large database of phonological inventories from the world's
languages, \citet[540]{Moran2012} defines a set of diacritic ordering
conventions. The conventions are influenced by the linguistic literature, though
some ad-hoc decisions had to be taken given the vast variability of phonological segments 
described by linguists.

@@

\begin{itemize}
	\item[] \textsc{Combining Diacritical Marks (above) ordering:}
	\begin{itemize}
	  \item[→] nasalized <ẽ>
	  \item[→] centralized <ë> \textbar{} mid-centralized <e̽>
	  \item[→] extra short <ĕ>
%	  \item[→] (tone accents, e.g. <è>)
	  \item[→] unreleased <p̚>
%	  \item[→] Spacing Modifier Letters, see above	  
 \end{itemize} \end{itemize}

@@

%\begin{table}[htdp]

 \topcaption{IPA letters with Unicode encodings}
 \label{tab:ipa_letters}
 \tablehead{\toprule & Code & Unicode name & IPA name \\ \midrule }
 \tabletail{\bottomrule}

@@

\begin{xtabular}{ l l L{4.5cm} L{4.5cm} }

@@

\charis{ⱱ} & \uni{2C71} & \textsc{latin small letter v with right hook} & voiced labiodental tap \\ 

@@

%\end{table}
